Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
LinearRegression -> LogisticRegression

As an example, let us consider a supervised learning task using linear regression.
Given the API defined above, solving this problem is as simple as:
\begin{center}
\texttt{clf = LinearRegression(penalty="l1").fit(X, y)}
\end{center}
In this snippet, a \texttt{LinearRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence enabling $L1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the arrays \texttt{X} and
\texttt{y}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LinearRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}. Let us also note that the snippet relies on the
fact that the \texttt{fit} method always returns the object it was called
on\footnote{I.e., the \texttt{self} argument it was called on.}, hence making
method chaining  possible.

@@

In our example, if one wanted to transform the inputs \texttt{X} before
fitting the linear regression estimator, e.g., by standardizing the feature values,
one could thus simply write:
\begin{center}
\texttt{X = StandardScaler().fit(X).transform(X)}
\end{center}

>>>>

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
\begin{center}
\texttt{clf = LogisticRegression(penalty="l1").fit(X\_train, y\_train)}
\end{center}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence enabling $L1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the training arrays \texttt{X\_train} and
\texttt{y\_train}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LogisticRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}. Let us also note that the snippet relies on the
fact that the \texttt{fit} method always returns the object it was called
on\footnote{I.e., the \texttt{self} argument it was called on.}, hence making
method chaining  possible.

@@

In our example, if one wanted to transform the inputs \texttt{X} before
fitting the logistic regression estimator, e.g., by standardizing the feature values,
one could thus simply write:
\begin{center}
\texttt{X = StandardScaler().fit(X).transform(X)}
\end{center}
